Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling

### 2019-05-29 latex/afm-cs-main.tex
Update on Overleaf.

Although BPDN is effective in the general setting, using it for reconstruction
from horizontal $\mu$-path samples often yields artifacts in the vertical
direction (that is, the direction orthogonal to the $\mu$-path scans) leading to
strong discontinuities in the image. These artifacts grow more prominent as the
length of the $\mu$-paths is increased \cite{maxwell2014compressed} as these
longer paths lead to increased mutual coherence between the measurement matrix
$R$ and the sparsity basis $U$. However, longer $\mu$-paths means fewer
tip re-engagements and thus shorter scan times.
\noindent 
\begingroup \setlength{\tabcolsep}{1pt}
\begin{figure*}[h!]
  \centering
  \begin{tabular}{cccccc}
    \textit{\small original image} & \textit{\small BPDN} & \textit{\small BPVV}
    & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
    % 
    \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_framed}
    %
    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu}
     % 
    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu}
     % 
    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_zoomin}
     % 
    &\includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu_zoomin}
    %
    &\includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu_zoomin}\\
    % 
    % ------------------------------ Row  2 --------------------------------------------
    \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_framed}
    %
    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu}
    %
    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu}
    %
    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_zoomin}
    %
    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu_zoomin}
    %
    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu_zoomin}
  \end{tabular}
  \caption{Reconstruction comparison between BPDN and BPVV. (first column)
    Original raster-scanned image. (second column) BPDN reconstruction from
    random, 40 pixel long $\mu$-paths with 25\% sampling. (third column) BPVV
    reconstruction from the same sub-sampled data. (remaining columns)
    Corresponding details from the red boxes indicated in the raster image. The
    results show that BPVV reduces the artifacts arising from the horizontal
    scans of the $\mu$-path pattern that appear in BPDN reconstructions.}
  \label{fig:BPTV_demonstration}
\end{figure*}
\todo{Re-do this figure???}
\endgroup

>>>>

Although BPDN is effective in the general setting, using it for reconstruction
from horizontal $\mu$-path samples often yields artifacts in the vertical
direction (that is, the direction orthogonal to the $\mu$-path scans) leading to
strong discontinuities in the image. These artifacts grow more prominent as the
length of the $\mu$-paths is increased \cite{maxwell2014compressed} as these
longer paths lead to increased mutual coherence between the measurement matrix
$R$ and the sparsity basis $U$. However, longer $\mu$-paths means fewer
tip re-engagements and thus shorter scan times.
\noindent 
\begingroup \setlength{\tabcolsep}{1pt}
\begin{figure*}[h!]
  \centering
  \begin{tabular}{cccccc}
    \textit{\small original image} & \textit{\small BPDN} & \textit{\small BPVV}
    & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
    % 
    \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_framed}
    %
    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu}
     % 
    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu}
     % 
    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_zoomin}
     % 
    &\includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu_zoomin}
    %
    &\includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu_zoomin}\\
    % 
    % ------------------------------ Row  2 --------------------------------------------
    \includesvg[width=0.16\textwidth]{figures/dna_og.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bp.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bptv.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_og_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bp_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bptv_zoom.svg}
  \end{tabular}
  \caption{Reconstruction comparison between BPDN and BPVV. (first column)
    Original raster-scanned image. (second column) BPDN reconstruction from
    random, 40 pixel long $\mu$-paths with 25\% sampling. (third column) BPVV
    reconstruction from the same sub-sampled data. (remaining columns)
    Corresponding details from the red boxes indicated in the raster image. The
    results show that BPVV reduces the artifacts arising from the horizontal
    scans of the $\mu$-path pattern that appear in BPDN reconstructions.}
  \label{fig:BPTV_demonstration}
\end{figure*}
\todo{Re-do this figure???}
\endgroup
